---
title: "betaNB: Bootstrap for Regression Effect Sizes"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betaNB: Bootstrap for Regression Effect Sizes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![CRAN Status](https://www.r-pkg.org/badges/version/betaNB)](https://cran.r-project.org/package=betaNB)
[![R-Universe Status](https://jeksterslab.r-universe.dev/badges/betaNB)](https://jeksterslab.r-universe.dev)
[![R-CMD-check](https://github.com/jeksterslab/betaNB/workflows/R-CMD-check/badge.svg)](https://github.com/jeksterslab/betaNB/actions)
[![test-coverage](https://github.com/jeksterslab/betaNB/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/jeksterslab/betaNB/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/jeksterslab/betaNB/actions/workflows/lint.yaml/badge.svg)](https://github.com/jeksterslab/betaNB/actions/workflows/lint.yaml)
[![codecov](https://codecov.io/gh/jeksterslab/betaNB/branch/main/graph/badge.svg?token=KVLUET3DJ6)](https://codecov.io/gh/jeksterslab/betaNB)
<!-- badges: end -->

## Description

Generates nonparametric bootstrap confidence intervals
(Efron & Tibshirani, 1993: https://doi.org/10.1201/9780429246593)
for standardized regression coefficients (beta)
and other effect sizes,
including multiple correlation, semipartial correlations,
improvement in R-squared, squared partial correlations,
and differences in standardized regression coefficients,
for models fitted by `lm()`.

## Installation

You can install the CRAN release of `betaNB` with:

```r
install.packages("betaNB")
```

You can install the development version of `betaNB` from
[GitHub](https://github.com/jeksterslab/betaNB) with:

```r
if (!require("remotes")) install.packages("remotes")
remotes::install_github("jeksterslab/betaNB")

## Example

In this example, a multiple regression model is fitted
using program quality ratings (`QUALITY`) as the regressand/outcome variable
and number of published articles attributed to the program faculty members (`NARTIC`),
percent of faculty members holding research grants (`PCTGRT`), and
percentage of program graduates who received support (`PCTSUPP`) as regressor/predictor variables
using a data set from 1982 ratings of 46 doctoral programs in psychology in the USA (National Research Council, 1982).
Confidence intervals for the standardized regression coefficients are generated
using the `BetaNB()` function from the `betaNB` package.

```{r}
#| message = FALSE
library(betaNB)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaNB"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaNB::nas1982
```

### Regression

Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

### Nonparametric Bootstrap

```{r}
nb <- NB(object)
```

### Standardized Regression Slopes

```{r}
BetaNB(nb)
```

### Other Effect Sizes

The `betaNB` package also has functions to generate nonparametric bootstrap confidence intervals
for other effect sizes such as
`RSqNB()` for multiple correlation coefficients (R-squared and adjusted R-squared),
`DeltaRSqNB()` for improvement in R-squared,
`SCorNB()` for semipartial correlation coefficients,
`PCorNB()` for squared partial correlation coefficients,
and
`DiffBetaNB()` for differences of standardized regression coefficients.

#### Multiple Correlation Coefficients (R-squared and adjusted R-squared)

```{r}
RSqNB(nb)
```

#### Improvement in R-squared

```{r}
DeltaRSqNB(nb)
```

#### Semipartial Correlation Coefficients

```{r}
SCorNB(nb)
```

#### Squared Partial Correlation Coefficients

```{r}
PCorNB(nb)
```

#### Differences of Standardized Regression Coefficients

```{r}
DiffBetaNB(nb)
```

### References

Efron, B., & Tibshirani, R. J. (1993).
*An introduction to the bootstrap*.
Chapman & Hall.
https://doi.org/10.1201/9780429246593

National Research Council. (1982).
*An assessment of research-doctorate programs in the United States: Social and behavioral sciences*.
https://doi.org/10.17226/9781.
Reproduced with permission from the National Academy of Sciences,
Courtesy of the National Academies Press, Washington, D.C.

Pesigan, I. J. A. (2022).
Confidence intervals for standardized coefficients:
Applied to regression coefficients in primary studies and indirect effects in meta-analytic structural equation modeling [Unpublished doctoral dissertation].
University of Macau. 
