---
title: "betaNB: Example Using the DiffBetaNB Function"
author: "Ivan Jacob Agaloos Pesigan"
output: rmarkdown::html_vignette
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
nocite: |
  @Pesigan-2022
  @Efron-Tibshirani-1993
vignette: >
  %\VignetteIndexEntry{betaNB: Example Using the DiffBetaNB Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Confidence intervals for
differences of standardized regression slopes
are generated using
the `DiffBetaNB()` function from the `betaNB` package.
In this example,
we use the data set and the model used in
[betaNB: Example Using the BetaNB Function](example-beta-nb.html).

```{r}
#| message = FALSE
library(betaNB)
```

```{r}
#| echo = FALSE
if (!exists("nas1982")) {
  try(
    data(
      "nas1982",
      package = "betaNB"
    ),
    silent = TRUE
  )
}
df <- nas1982
```

```{r}
#| eval = FALSE
df <- betaNB::nas1982
```

### Regression

Fit the regression model using the `lm()` function.

```{r}
object <- lm(QUALITY ~ NARTIC + PCTGRT + PCTSUPP, data = df)
```

### Nonparametric Bootstrap

```{r}
nb <- NB(object)
```

### Differences of Standardized Regression Slopes

#### Normal-Theory Approach

```{r}
out <- DiffBetaNB(nb, alpha = 0.05)
```

## Methods

### summary

Summary of the results of `DiffBetaNB()`.

#### Percentile Confidence Intervals

```{r}
summary(out, type = "pc")
```

#### Bias Corrected Confidence Intervals

```{r}
summary(out, type = "bc")
```

#### Bias Corrected and Accelerated Confidence Intervals

```{r}
summary(out, type = "bca")
```

### coef

Return the vector of estimates.

```{r}
coef(out)
```

### vcov

Return the sampling covariance matrix.

```{r}
vcov(out)
```

### confint

Return confidence intervals.

#### Percentile Confidence Intervals

```{r}
confint(out, level = 0.95, type = "pc")
```

#### Bias Corrected Confidence Intervals

```{r}
confint(out, level = 0.95, type = "bc")
```

#### Bias Corrected and Accelerated Confidence Intervals

```{r}
confint(out, level = 0.95, type = "bca")
```

## References
